Beyond clines: lineages and haplotype blocks in hybrid zones

### 2016-04-26 drafts/supplement.tex
peter edited through

\begin{figure}
    \includegraphics{figs/alleleFrequencies_sim.pdf}
    \caption{
    Frequency of ancestry $B$,
    across geography at different physical positions on the genome, simulated for a hybrid zone
     $T=100$ generations after secondary contact, with $s=0.1$,
     using 50 demes, each with 500 diploid individuals and $\sigma=1$.
    Each line represents a locus some distance $r$ away from the true target of selection with colors corresponding to different values of $r$, transitioning from red (tight linkage to selected site) to blue (distantly linked).
    Grey lines represent the same positions from a simulation with
    identical parameters except that $s=0$. 
    Corresponding theoretical quantities are shown juxtaposed in Figure \ref{sfig:alleleFreq_tau100_comparison};
    the same plot is shown with weaker selection in Figure \ref{alleleFreq_tau100_weaker_s} and at a longer time in Figure \ref{alleleFreq_tau1000}.
}\label{alleleFreq_tau100}
\end{figure}

@@

\begin{figure}
    \includegraphics{{figs/simulation_SIGMA1_Ninds25000_ndemes50_s0.01_tau1000_blocksAlongChromAncBConditioning_nonnormalized}.pdf}
    \caption{
        \textbf{Mean haplotype lengths of $B$ haplotypes}, $l_B(x,m)$,
        across the genome (horizontal axis) and at differntial spatial locations (colored lines),
        from a simulation with 50 demes having 500 individuals each, $s=0.01$, $\sigma=1$, and after $T=1000$ generations.
    } \label{sfig:blocksAlongChromAncBConditioning_nonnormalized}
\end{figure}

@@

\begin{figure}
\includegraphics{figs/blocksAlongChromAncBConditioning.pdf}
\caption{
    \textbf{Normalized mean enclosing block length}, $l_B(m,x)$, after $T=1000$ generations,
    against position relative to the selected locus (horizontal axis)
    located in the center of a 1M chromosome.
    Each line shows the mean block length at that spatial and genomic position
    divided by the mean over the chromosome at that location;
    the simulation was run with $s=1$ and $\sigma=1$,
    50 demes, each containing 500 diploid individuals.
}\label{Fig:blockLengths}
\end{figure}

@@

\begin{figure}
\includegraphics{figs/ratioAdjacentBlocksAlongChromAncBConditioning.pdf}
\caption{Ratio $\frac{2\sum{l_B(m_i)}}{\sum{l_A(m_i-)+I_A(m_i+)}}$ of mean block length and adjacent block lengths across a simulated chromosome with a single underdominant site and conditioning on ancestry $B$ at the selected site ($s=0.01, T=1000$).  Each line represents a deme and is normalized by mean block length across the chromosome in the deme.}\label{Supp:ratioBlockAdjacent}
\end{figure}

\begin{figure}
\includegraphics{figs/ratioAdjacentBlocksAlongChromHeatmapAncBConditioning.pdf}
\caption{Heatmap of $\frac{2\sum{l_B(m_i)}}{\sum{l_A(m_i-)+I_A(m_i+)}}$ across a simulated chromosome with a single underdominant site and conditioning on ancestry $B$ at the selected site ($s=0.01, T=1000$). }\label{Supp:ratioBlockAdjacentHeatmap}
\end{figure}

>>>>

\begin{figure}
    \includegraphics{figs/alleleFrequencies_sim.pdf}
    \caption{
    Frequency of ancestry $B$,
    across geography at different physical positions on the genome, simulated for a hybrid zone
     $T=100$ generations after secondary contact, with $s=0.1$,
     using 50 demes, each with 500 diploid individuals and $\sigma=1$.
    Each line represents a locus some distance $r$ away from the true target of selection with colors corresponding to different values of $r$, transitioning from red (tight linkage to selected site) to blue (distantly linked).
    Grey lines represent the same positions from a simulation with
    identical parameters except that $s=0$. 
    Corresponding theoretical quantities are shown juxtaposed in Figure \ref{fig:alleleFreq_tau100_comparison};
    the same plot is shown with weaker selection in Figure \ref{alleleFreq_tau100_weaker_s} and at a longer time in Figure \ref{alleleFreq_tau1000}.
}\label{alleleFreq_tau100}
\end{figure}

@@

\begin{figure}
    \includegraphics{{figs/simulation_SIGMA1_Ninds25000_ndemes50_s0.01_tau1000_blocksAlongChromAncBConditioning_nonnormalized}.pdf}
    \caption{
        \textbf{Mean haplotype lengths of $B$ haplotypes}, $l_B(x,m)$,
        across the genome (horizontal axis) and at different spatial locations (colored lines),
        from a simulation with 50 demes having 500 individuals each, $s=0.01$, $\sigma=1$, and after $T=1000$ generations.
    } \label{sfig:blocksAlongChromAncBConditioning_nonnormalized}
\end{figure}

@@

\begin{figure}
\includegraphics{figs/blocksAlongChromAncBConditioning.pdf}
\caption{
    \textbf{Normalized mean enclosing block length}, $\bar l_B(m,x)$, after $T=1000$ generations,
    against position relative to the selected locus (horizontal axis)
    located in the center of a 1M chromosome.
    Each line shows the mean block length at that spatial and genomic position
    divided by the mean over the chromosome at that location;
    the simulation was run with $s=1$ and $\sigma=1$,
    50 demes, each containing 500 diploid individuals.
}\label{Fig:blockLengths}
\end{figure}

@@

\begin{figure}
\includegraphics{figs/ratioAdjacentBlocksAlongChromAncBConditioning.pdf}
    \caption{The statistic $\bar C(m,x)$: the ratio $\frac{2\sum{l_B(m_i)}}{\sum{l_A(m_i-)+I_A(m_i+)}}$ of mean block length and mean adjacent block lengths across a simulated chromosome with a single underdominant site and conditioning on ancestry $B$ at the selected site ($s=0.01, T=1000$).  Each line represents a deme and is normalized by mean block length across the chromosome in the deme.}\label{Supp:ratioBlockAdjacent}
\end{figure}

\begin{figure}
\includegraphics{figs/ratioAdjacentBlocksAlongChromHeatmapAncBConditioning.pdf}
    \caption{Heatmap of $C(m,x)=\frac{2\sum{l_B(m_i)}}{\sum{l_A(m_i-)+I_A(m_i+)}}$ across a simulated chromosome with a single underdominant site and conditioning on ancestry $B$ at the selected site ($s=0.01, T=1000$). }\label{Supp:ratioBlockAdjacentHeatmap}
\end{figure}
